\bf Forecasts Reconciliation: A geometric view with new insights on bias correction.

### 2019-08-22 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
Rewrite the empirical section and modified some schematics in section 3 and 4

	To clarify these concepts consider the example of the hierarchy in Figure~\ref{fig:basichier}.  For this hierarchy, $n=7$, $\bm{y}_t = [y_{Tot,t},y_{A,t}, y_{B,t},y_{C,t},y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$, $m=4$, $\bm{b}_t = [y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$ and
	\[
	\bm{S} = \begin{pmatrix}
	1 & 1 & 1 & 1  \\
	1 & 1 & 0 & 0 \\
	0 & 0 & 1 & 1 \\
	& \multicolumn{2}{c}{\bm{I}_4} &
	\end{pmatrix},
	\]
	where $\bm{I}_4$ is the $4\times 4$ identity matrix.

@@

     To further illustrate, Figure \ref{fig:3D_hierarchy} depicts the most simple three variable hierarchy where $y_{Tot,t}=y_{A,t}+y_{B,t}$.  The coherent subspace is depicted as a grey $2$-dimensional plane within $3$-dimensional space, i.e. $m=2$ and $n=3$.  It is worth noting that the coherent subspace is spanned by the columns of $\bm{S}$, i.e.\ $\mathfrak{s}=\text{span}(\bm{S})$.  In Figure~\ref{fig:3D_hierarchy}, these columns are $\vec{s}_1=(1,1,0)'$ and $\vec{s}_2=(1,0,1)'$.  However, it is equally important to recognise that the hierarchy could also have been defined in terms of $y_{Tot,t}$ and $y_{A,t}$ rather than the bottom level series, $y_{A,t}$ and $y_{B,t}$. In this case the corresponding `$\bm{S}$ matrix' would have columns $(1,0,1)'$ and $(0,1,-1)'$.  However, while there are multiple ways to define an $\bm{S}$ matrix, in all cases the columns will span the same coherent subspace, which is unique.

@@

	 Despite the common use of the term {\em hierarchical time series}, it should be clear from the definition that the data need not necessarily follow a hierarchy.  Also notable by its absence in the above definition is any reference to {\em aggregation}. In some ways, terms such as {\em hierarchical} and {\em aggregation} can be misleading since the literature has covered instances that cannot be depicted in a similar fashion to Figure~\ref{fig:basichier} and/or do not involve aggregation. {\bf Include brief summary of all non-traditional hierarchies - e.g. grouped hierarchies, temporal hierarchies with weird overlapping, problems where we look at differences between variables etc.}  Finally, although Definition~\ref{def:cohspace} makes reference to time series, this definition can be easily generalised to any vector-valued data for which some linear constraints are known to hold for all realisations.

%	It will sometimes be useful to think of pre-multiplication by $\bm{S}$ as a mapping from $\mathbb{R}^m$ to $\mathbb{R}^n$, in which case we use the notation $s(.)$. Although the codomain of $s(.)$ is $\mathbb{R}^n$, its image is the coherent space $\mathfrak{s}$ as depicted in Figure~\ref{fig2}.
%	
%	\begin{figure}[H]
%		\begin{center}
%			\begin{tikzpicture}[
%			>=stealth,
%			bullet/.style={
%				fill=black,
%				circle,
%				minimum width=1.5cm,
%				inner sep=0pt
%			},
%			projection/.style={
%				->,
%				thick,
%				label,
%				shorten <=2pt,
%				shorten >=2pt
%			},
%			every fit/.style={
%				ellipse,
%				draw,
%				inner sep=0pt
%			}
%			]
%			\node at (2,3) {$s$};
%			\node at (0,5) {$\mathbb{R}^m$(domain of $s$)};
%			\node at (4,5) {$\mathbb{R}^n$(codomain of $s$)};
%			\node at (4.7,2.0) {$\mathfrak{s}$(image of $s$)};
%			%\node[bullet,label=below:$f(x)$] at (4,2.5){};
%			\draw (0,2.5) ellipse (1.02cm and 2.2cm);
%			\draw (4,2.5) ellipse (1.02cm and 2.2cm);
%			\draw (4,2.5) ellipse (0.51cm and 1.1cm);
%			\draw[projection, label=below:$f$] (0.3,2.5) -- (3.8,2.5) ;
%			\end{tikzpicture}
%		\end{center}
%		\caption{The domain, codomain and image of the mapping $s$.}\label{fig2}
%	\end{figure}

@@

	The simple geometric intuition behind the proof is demonstrated in Figure~\ref{fig:Schematic_OLSRecon}.  In this schematic, the coherent subspace is depicted as a black arrow.  The base forecast $\hat{\bm{y}}$ is shown as a blue dot.  Since $\hat{\bm{y}}$ is incoherent, $\hat{\bm{y}}_{t+h|t}\notin\mathfrak{s}$ and in this case the inequality is strict.  Reconciliation is an orthogonal projection from $\hat{\bm{y}}$ to the coherent subspace yielding the reconciled forecast $\tilde{\bm{y}}$ shown in red.  Finally, the target of the forecast $\bm{y}$ is displayed as a black point, and although its exact location is unknown to the forecaster, it is known that it will lie somewhere along the coherent subspace.

@@

	Figure~\ref{fig:Schematic_OLSRecon} clearly shows that $\hat{\bm{y}}$, $\tilde{\bm{y}}$ and $\bm{y}$ form a right angled triangle with $\tilde{y}$ at the right-angled vertex.  In this triangle the line between $\bm{y}$ and $\hat{\bm{y}}$ is the hypotenuse and therefore must be longer than the distance between $\bm{y}$ and $\tilde{\bm{y}}$.  As such reconciliation is guaranteed to reduce the squared error of the forecast.

@@

	{\bf Discuss results in Figure 11 here}

@@

	Figure~\ref{fig:MinT_justification1} provides geometrical intuition into the MinT method.  Suppose the in-sample errors are given by the orange points.  They provide information on the most likely direction of large deviations from the coherent subspace.  This direction is denoted by $\bm{R}$.  Figure~\ref{fig:MinT_justification2} then shows a target value of $\bm{y}$, while the grey points indicate possible values for the base forecasts (the base forecasts are of course stochastic).  One possible value of the forecast is depicted in blue as $\hat{\bm{y}}$.  An oblique projection of the blue point back along the direction of $\bm{R}$ yields a reconciled forecast closer to the target, especially compared to an orthogonal projection showed as in Figure \ref{fig:Orthogonal_projection_all_points}.  Figure \ref{fig:Oblique_projection_all_points} depicts a similar oblique projection along $\bm{R}$ for all the gray points yield reconciled forecasts tightly packed near the target $\bm{y}$.  In this sense, the oblique MinT projection minimises the forecast error variance of reconciled forecasts. In contrast to the result in Theorem~\ref{th:gdistred}, this property is a statistical property in the sense that MinT is optimal in expectation.

	\begin{figure}[H]
		\centering
		%\vspace{-0.9cm}
		\small
		\resizebox{\linewidth}{!}{
			\input{Figs/insampledir}
		}
		\caption{A schematic to represent MinT reconciliation. Points in orange colour represent the insample errors. $\bm{R}$ shows the most likely direction of deviations from the coherent subspace. $\hat{\bm{y}}$ is projected onto $\mathfrak{s}$ along the the direction of $\bm{R}$.}\label{fig:MinT_justification1}
	\end{figure}

	\begin{figure}[H]
		\centering
		%\vspace{-0.9cm}
		\small
		\resizebox{\linewidth}{!}{
			\input{Figs/oblique_justification2}
		}
		\caption{A schematic to represent MinT reconciliation. Grey points indicate potential realisations of the base forecast while the blue dot indicates one such realisation. The black dot ${\bm y}$ denotes the (unknown) target of the forecast.}\label{fig:MinT_justification2}
	\end{figure}

	\begin{figure}[H]
		\centering
		%\vspace{-0.9cm}
		\small
		\resizebox{\linewidth}{!}{
			\includegraphics{Figs/OrthProj.pdf}}
		\caption{All gray points are orthogonally projected onto the coherent subspace $\mathfrak{s}$. Reconciled forecasts marked in red dots are widely spread about the target $\bm{y}$.}\label{fig:Orthogonal_projection_all_points}
	\end{figure}

	\begin{figure}[H] 
	\centering
	%\vspace{-0.9cm}
	\small
	\resizebox{\linewidth}{!}{
		\includegraphics{Figs/ObliqueProjection.pdf}}
	\caption{All gray points are obliquely projected along the direction of $\bm{R}$. Reconciled points denoted in red dots are concentrated about the target $\bm{y}$.}\label{fig:Oblique_projection_all_points}
	\end{figure}

@@

	We note that the above result holds when the projection $\bm{SG}$ has the coherent subspace $\mathfrak{s}$ as its image and not for all projection matrices in general. To describe this more explicitly suppose $\bm{SG}$ has as its image  $\mathfrak{L}$ which is itself a lower dimensional linear subspace of $\mathfrak{s}$, i.e. $\mathfrak{L}\subset\mathfrak{s}$. Then for $\left\{\bm{\mu}_{t+h|t}:\bm{\mu}_{t+h|t}\in\mathfrak{s},\bm{\mu}_{t+h|t}\notin\mathfrak{L}\right\}$,  $\bm{S}\bm{G}\bm{\mu}_{t+h|t} \ne \bm{\mu}_{t+h|t}$. This is depicted in Figure~\ref{fig:Schematic_3D} where $\bm{\mu}_{t+h|t}$ is projected to a point $\bar{\bm{\mu}}$ in $\mathfrak{L}$.  In this case, the expectation of reconciled forecast will be $\bar{\bm{\mu}}$ rather than $\bm{\mu}_{t+h|t}$ and hence biased.

@@

	Finally, it is often stated that an assumption required to prove the unbiasedness preserving property is that $\bm{SGS}=\bm{S}$ or alternatively that $\bm{GS}=\bm{I}$.  Both of these conditions are equivalent to assuming that $\bm{SG}$ is a projection matrix.  \todo{perhaps elaborate in a proof in appendix}  However, problems arise when viewing the preservation of unbiasedness through the prism of imposing a constraint $\bm{GS}=\bm{I}$. This thinking suggests that a way to deal with biased forecasts is to select $\bm{G}$ in an unconstrained manner.  However, equipped with a geometric understanding of the problem, we would advise against this approach.  The constraint $\bm{GS}=\bm{I}$  is not just about bias and dropping the constraint compromises all of the attractive properties of projections.  Opening the door to reconciliation methods that change already coherent base forecast would seem to suggest an increase in the variability of the forecast.  This seems particularly perverse when the motivation for using a biased method in the first place is to reduce variance is to reduce variance.

@@

	Alternatively, a more general purpose approach to bias correction is to simply estimate the bias by taking the sample mean of $\bm{y
	}_{t+h}-\hat{\bm{y}}_{t+h|t}$ for all $t+h$ in the training sample.  This can be then subtracted from future forecasts.  As stated in the discussion of MinT, in-sample errors are already used to estimate the optimal direction of projection.  As such we see no problems with using the same errors to bias correct.  Geometrically, the intuition is simple.  In Figure~\ref{fig:MinT_justification1}, the orange points are centered around the origin as would be expected from an unbiased forecast.  If forecasts are biased, then errors should simply be translated until they are centered at the origin.

@@

	Total tourism flow of any country can naturally disaggregate along a geographical hierarchy. Producing accurate forecasts for these hierarchical time series while preserving the coherency is important for making align business decisions in the tourism industry. Many applications related to Australian tourism flow have pronounced that reconciliation improves the point forecast accuracy (\cite{Athanasopoulos2009}, \cite{Hyndman2011}, \cite{WicEtAl2019}).

	Using a similar empirical application to tourism forecasting in Australia, we show how to use projection-based reconciliation when we have a set of biased incoherent forecasts. As we mentioned in the previous section our focus is to bias adjust the incoherent forecasts first and then do the reconciliation.

	\subsubsection*{Data:}
	We use ``overnight trips" as a measure of domestic tourism flow in Australia. Total ``overnight trips" in Australia can be disaggregated into 7 states, 27 zones and 75 regions forming a geographical hierarchy with $110$ total number of series and $75$ bottom level series. More information about the series of this hierarchy is given in Table \ref{table:A1} in the appendix. Data were obtained from the National Visitor Survey (NVS) which were collected through telephone interviews from an annual sample of $120,000$ Australian residents aged $15$ years or more. Data form a monthly series starting from January 1998 to December 2017 which gives a total of $240$ observations per series.

	We produce $h=1$ to $h=6$ months ahead forecasts using a rolling window approach. First training window of $100$ observations is considered from Jan-$1998$ to Apr-$2006$ and produce forecasts for May-$2006$ to Oct-$2006$. Then we roll the training window one month at a time where the final forecast is produced for Dec-$2017$. This directs to $140 \quad 1$-step-ahead, $139 \quad 2$-step-ahead through $135 \quad 6$-step-ahead forecasts left for evaluation.

	\subsubsection*{Preliminary analysis:}

	While observing the patterns of individual series, we noticed that the signal-to-noise ratio decreases with the disaggregate level of the hierarchy. From Figure \ref{fig:Total_TSplots} and \ref{fig:States_Zones_Regs_TSplots} this is depicted well as we see much noisier series in bottom levels whereas the noise level is comparatively stabilised in the upper levels. We have also observed that the overnight trips for `Adelaide Hills` has an anomalous observation on December-2002. We replaced this observation with the average overnight trips on December-2001 and December-2003 for the same destination.

	\begin{figure}
		\centering
		\small
		\includegraphics[width = \textwidth]{Empirical-results/TS-plots/Total_TSplot.pdf}
		\caption{Time plot for total overnight trips.}\label{fig:Total_TSplots}
	\end{figure}

	\begin{figure}
		\centering
		\small
		\includegraphics[width = \textwidth]{Empirical-results/TS-plots/States_Zones_Regs_TSplots.pdf}
		\caption{Time plot for some selected series from different disaggregate levels of the hierarchy.}\label{fig:States_Zones_Regs_TSplots}
	\end{figure}

	\subsubsection*{Base forecasts and reconciliation:}

	We first transform each series in the hierarchy using the Box-Cox transformation as given in equation (\ref{eq:BoxCox_transformation}) to stabilise any variations in the data.

	\begin{equation} \label{eq:BoxCox_transformation}
	x_t = 
	\begin{cases} 
	\log(y_t) & \text{if } \lambda = 0 \\
	\frac{y_t^\lambda - 1}{\lambda}  & \text{if } \lambda \ne 0
	\end{cases}
	\end{equation}

	We use "guerrero" method \citep{guerrero1993time} implemented in \verb|BoxCox.lambda()| function in \verb|forecast| package R software \citep{Rforecast} to select optimal $\lambda$. Then  we fit univariate ARIMA models for the transformed series. We use \verb|auto.arima()| function in \verb|forecast| package to choose the best model that minimises the AIC. Using the fitted models we produce $h=1,...,6$ months ahead forecasts for each series in the hierarchy. These forecasts are then back-transformed using equation (\ref{eq:BoxCox_back-transformation}) to scale them back into the original space. However, the back transformed forecasts will be biased \citep{FPP2018}.

	\begin{equation} \label{eq:BoxCox_back-transformation}
	y_{t+h} = 
	\begin{cases} 
	\exp({x_{t+h}}) & \text{if } \lambda = 0 \\
	(\lambda x_{t+h} + 1)^{1/\lambda}  & \text{if } \lambda \ne 0
	\end{cases}
	\end{equation}

	Hence the reconciled forecasts follow from these will also biased. This is the exact scenario that we want to demonstrate in this study. As we proposed before, we first bias correct the base forecasts prior to the reconciliation. We use the mathematical formula in equation (\ref{eq:BoxCox_BT_biasadj}) to calculate the back-transformed and bias-adjusted forecasts.

	\begin{equation} \label{eq:BoxCox_BT_biasadj}
	 y_{t+h} = 
	\begin{cases} 
	\exp({x_{t+h}})[1+\frac{\sigma_h^2}{2}] & \text{if } \lambda = 0 \\
	(\lambda x_{t+h} + 1)^{1/\lambda}[1 + \frac{\sigma_h^2(1-\lambda)}{2(\lambda x_{t+h} + 1)^2}]       & \text{if } \lambda \ne 0
	\end{cases}
	\end{equation}
	where, $x_{t+h}$ is the $h$-step-ahead forecasts from the Box-Cox transformed series and $\sigma_h^2$ is the variance of $x_{t+h}$.

	Once we get the base forecasts for all series in the hierarchy, we can do the projection-based reconciliation to get coherent forecasts. We reconcile both biased and bias-corrected (unbiased) base forecasts to demonstrate how the reconciliation follows from unbiased base forecasts improves the forecast accuracy. MinT(Shrink), WLS, OLS and bottom-up methods are used for reconciliation.

	\subsubsection*{Results and discussion:}

>>>>

	To clarify these concepts consider the example of the hierarchy in Figure \ref{fig:basichier}.  For this hierarchy, $n=7$, $\bm{y}_t = [y_{Tot,t},y_{A,t}, y_{B,t},y_{C,t},y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$, $m=4$, $\bm{b}_t = [y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$ and
	\[
	\bm{S} = \begin{pmatrix}
	1 & 1 & 1 & 1  \\
	1 & 1 & 0 & 0 \\
	0 & 0 & 1 & 1 \\
	& \multicolumn{2}{c}{\bm{I}_4} &
	\end{pmatrix},
	\]
	where $\bm{I}_4$ is the $4\times 4$ identity matrix.

@@

     To further illustrate, Figure \ref{fig:3D_hierarchy} depicts the most simple three variable hierarchy where $y_{Tot,t}=y_{A,t}+y_{B,t}$.  The coherent subspace is depicted as a grey $2$-dimensional plane within $3$-dimensional space, i.e. $m=2$ and $n=3$.  It is worth noting that the coherent subspace is spanned by the columns of $\bm{S}$, i.e.\ $\mathfrak{s}=\text{span}(\bm{S})$.  In Figure \ref{fig:3D_hierarchy}, these columns are $\vec{s}_1=(1,1,0)'$ and $\vec{s}_2=(1,0,1)'$.  However, it is equally important to recognise that the hierarchy could also have been defined in terms of $y_{Tot,t}$ and $y_{A,t}$ rather than the bottom level series, $y_{A,t}$ and $y_{B,t}$. In this case the corresponding `$\bm{S}$ matrix' would have columns $(1,0,1)'$ and $(0,1,-1)'$.  However, while there are multiple ways to define an $\bm{S}$ matrix, in all cases the columns will span the same coherent subspace, which is unique.

@@

	 Despite the common use of the term {\em hierarchical time series}, it should be clear from the definition that the data need not necessarily follow a hierarchy.  Also notable by its absence in the above definition is any reference to {\em aggregation}. In some ways, terms such as {\em hierarchical} and {\em aggregation} can be misleading since the literature has covered instances that cannot be depicted in a similar fashion to Figure\ref{fig:basichier} and/or do not involve aggregation. {\bf Include brief summary of all non-traditional hierarchies - e.g. grouped hierarchies, temporal hierarchies with weird overlapping, problems where we look at differences between variables etc.}  Finally, although Definition~\ref{def:cohspace} makes reference to time series, this definition can be easily generalised to any vector-valued data for which some linear constraints are known to hold for all realisations.

%	It will sometimes be useful to think of pre-multiplication by $\bm{S}$ as a mapping from $\mathbb{R}^m$ to $\mathbb{R}^n$, in which case we use the notation $s(.)$. Although the codomain of $s(.)$ is $\mathbb{R}^n$, its image is the coherent space $\mathfrak{s}$ as depicted in Figure \ref{fig2}.
%	
%	\begin{figure}[H]
%		\begin{center}
%			\begin{tikzpicture}[
%			>=stealth,
%			bullet/.style={
%				fill=black,
%				circle,
%				minimum width=1.5cm,
%				inner sep=0pt
%			},
%			projection/.style={
%				->,
%				thick,
%				label,
%				shorten <=2pt,
%				shorten >=2pt
%			},
%			every fit/.style={
%				ellipse,
%				draw,
%				inner sep=0pt
%			}
%			]
%			\node at (2,3) {$s$};
%			\node at (0,5) {$\mathbb{R}^m$(domain of $s$)};
%			\node at (4,5) {$\mathbb{R}^n$(codomain of $s$)};
%			\node at (4.7,2.0) {$\mathfrak{s}$(image of $s$)};
%			%\node[bullet,label=below:$f(x)$] at (4,2.5){};
%			\draw (0,2.5) ellipse (1.02cm and 2.2cm);
%			\draw (4,2.5) ellipse (1.02cm and 2.2cm);
%			\draw (4,2.5) ellipse (0.51cm and 1.1cm);
%			\draw[projection, label=below:$f$] (0.3,2.5) -- (3.8,2.5) ;
%			\end{tikzpicture}
%		\end{center}
%		\caption{The domain, codomain and image of the mapping $s$.}\label{fig2}
%	\end{figure}

@@

	The simple geometric intuition behind the proof is demonstrated in Figure \ref{fig:Schematic_OLSRecon}.  In this schematic, the coherent subspace is depicted as a black arrow.  The base forecast $\hat{\bm{y}}$ is shown as a blue dot.  Since $\hat{\bm{y}}$ is incoherent, $\hat{\bm{y}}_{t+h|t}\notin\mathfrak{s}$ and in this case the inequality is strict.  Reconciliation is an orthogonal projection from $\hat{\bm{y}}$ to the coherent subspace yielding the reconciled forecast $\tilde{\bm{y}}$ shown in red.  Finally, the target of the forecast $\bm{y}$ is displayed as a black point, and although its exact location is unknown to the forecaster, it is known that it will lie somewhere along the coherent subspace.

@@

	Figure \ref{fig:Schematic_OLSRecon} clearly shows that $\hat{\bm{y}}$, $\tilde{\bm{y}}$ and $\bm{y}$ form a right angled triangle with $\tilde{y}$ at the right-angled vertex.  In this triangle the line between $\bm{y}$ and $\hat{\bm{y}}$ is the hypotenuse and therefore must be longer than the distance between $\bm{y}$ and $\tilde{\bm{y}}$.  As such reconciliation is guaranteed to reduce the squared error of the forecast.

@@

	{\bf Discuss results in Figure 4 here}

	\begin{figure}[H]
		\centering
		\small
		\includegraphics[width = \textwidth]{Figs/BaseVsRecon_Emp_results.pdf}
		\caption{Difference of MSE between Base forecasts and reconciled forecasts over the replications is presented. Positive values of the difference implies reconciliation improves the forecast accuracy than base forecasts.}\label{fig:BaseVSRecon_Fc}
	\end{figure}

@@

	Figure \ref{fig:MinT_justification1} provides geometrical intuition into the MinT method.  Suppose the in-sample errors are given by the orange points.  They provide information on the most likely direction of large deviations from the coherent subspace.  This direction is denoted by $\bm{R}$.  Figure \ref{fig:MinT_justification2} then shows a target value of $\bm{y}$, while the grey points indicate possible values for the base forecasts (the base forecasts are of course stochastic).  One possible value of the forecast is depicted in blue as $\hat{\bm{y}}$.  An oblique projection of the blue point back along the direction of $\bm{R}$ yields a reconciled forecast closer to the target, especially compared to an orthogonal projection showed as in Figure \ref{fig:Orthogonal_projection_all_points}.  Figure \ref{fig:Oblique_projection_all_points} depicts a similar oblique projection along $\bm{R}$ for all the gray points yield reconciled forecasts tightly packed near the target $\bm{y}$.  In this sense, the oblique MinT projection minimises the forecast error variance of reconciled forecasts. In contrast to the result in Theorem~\ref{th:gdistred}, this property is a statistical property in the sense that MinT is optimal in expectation.

%	\begin{figure}[H]
%		\centering
%		%\vspace{-0.9cm}
%		\small
%		\resizebox{\linewidth}{!}{
%			\input{Figs/insampledir}
%		}
%		\caption{A schematic to represent MinT reconciliation. Points in orange colour represent the insample errors. $\bm{R}$ shows the most likely direction of deviations from the coherent subspace. $\hat{\bm{y}}$ is projected onto $\mathfrak{s}$ along the the direction of $\bm{R}$.}\label{fig:MinT_justification1}
%	\end{figure}
%		
%	\begin{figure}[H]
%		\centering
%		%\vspace{-0.9cm}
%		\small
%		\resizebox{\linewidth}{!}{
%			\input{Figs/oblique_justification2}
%		}
%		\caption{A schematic to represent MinT reconciliation. Grey points indicate potential realisations of the base forecast while the blue dot indicates one such realisation. The black dot ${\bm y}$ denotes the (unknown) target of the forecast.}\label{fig:MinT_justification2}
%	\end{figure}
%	
%	\begin{figure}[H]
%		\centering
%		%\vspace{-0.9cm}
%		\small
%		\resizebox{\linewidth}{!}{
%			\includegraphics{Figs/OrthProj.pdf}}
%		\caption{All gray points are orthogonally projected onto the coherent subspace $\mathfrak{s}$. Reconciled forecasts marked in red dots are widely spread about the target $\bm{y}$.}\label{fig:Orthogonal_projection_all_points}
%	\end{figure}
%	
%	
%	\begin{figure}[H] 
%	\centering
%	%\vspace{-0.9cm}
%	\small
%	\resizebox{\linewidth}{!}{
%		\includegraphics{Figs/ObliqueProjection.pdf}}
%	\caption{All gray points are obliquely projected along the direction of $\bm{R}$. Reconciled points denoted in red dots are concentrated about the target $\bm{y}$.}\label{fig:Oblique_projection_all_points}
%	\end{figure}

%%%%%%%%%%%%%%%%%%%

	\begin{figure}
		\centering
		\begin{subfigure}[t]{0.45\textwidth}
			\centering
			\includegraphics[width=\linewidth]{Figs/InsampDir_1.pdf} 
%			\label{fig:InsampDir_1}
		\end{subfigure}
		\hfill
		\begin{subfigure}[t]{0.45\textwidth}
			\centering
			\includegraphics[width=\linewidth]{Figs/InsampDir_2.pdf} 
%			\label{fig:InsampDir_2}
		\end{subfigure}

		\vspace{1cm}

		\begin{subfigure}[t]{0.45\textwidth}
			\centering
			\includegraphics[width=\linewidth]{Figs/OrthProj.pdf} 
%			\label{fig:OrthProj}
		\end{subfigure}
		\hfill
		\begin{subfigure}[t]{0.5\textwidth}
			\centering
			\includegraphics[width=\linewidth]{Figs/ObliqProj.pdf} 
%			\label{fig:ObliqProj}
		\end{subfigure}

%		\begin{subfigure}[t]{\textwidth}
%			\centering
%			\includegraphics[width=\linewidth]{example-image-c.pdf} 
%			\caption{Price regulation} \label{fig:timing3}
%		\end{subfigure}
		\caption{A schematic to represent orthogonal and oblique reconciliation.  Points in orange colour in top left figure represent the insample errors. $\bm{R}$ shows the most likely direction of deviations from the coherent subspace $\mathfrak{s}$. Grey points in top right figure indicate  potential realisations of the base forecast while the blue dot ${\hat{\bm y}}$ indicates one such realisation. The black dot ${\bm y}$ denotes the (unknown) target of the forecast. Bottom left figure shows the orthogonal projection of all potential realisations onto the coherent subspace while bottom right figure shows the oblique projection.} \label{fig:OthogonalVSOblique_projection}
	\end{figure}

@@

	We note that the above result holds when the projection $\bm{SG}$ has the coherent subspace $\mathfrak{s}$ as its image and not for all projection matrices in general. To describe this more explicitly suppose $\bm{SG}$ has as its image  $\mathfrak{L}$ which is itself a lower dimensional linear subspace of $\mathfrak{s}$, i.e. $\mathfrak{L}\subset\mathfrak{s}$. Then for $\left\{\bm{\mu}_{t+h|t}:\bm{\mu}_{t+h|t}\in\mathfrak{s},\bm{\mu}_{t+h|t}\notin\mathfrak{L}\right\}$,  $\bm{S}\bm{G}\bm{\mu}_{t+h|t} \ne \bm{\mu}_{t+h|t}$. This is depicted in Figure \ref{fig:Schematic_3D} where $\bm{\mu}_{t+h|t}$ is projected to a point $\bar{\bm{\mu}}$ in $\mathfrak{L}$.  In this case, the expectation of reconciled forecast will be $\bar{\bm{\mu}}$ rather than $\bm{\mu}_{t+h|t}$ and hence biased.

@@

	Finally, it is often stated that an assumption required to prove the unbiasedness preserving property is that $\bm{SGS}=\bm{S}$ or alternatively that $\bm{GS}=\bm{I}$.  Both of these conditions are equivalent to assuming that $\bm{SG}$ is a projection matrix.  \todo{perhaps elaborate in a proof in appendix}  However, problems arise when viewing the preservation of unbiasedness through the prism of imposing a constraint $\bm{GS}=\bm{I}$. This thinking suggests that a way to deal with biased forecasts is to select $\bm{G}$ in an unconstrained manner.  However, equipped with a geometric understanding of the problem, we would advise against this approach.  The constraint $\bm{GS}=\bm{I}$  is not just about bias and dropping the constraint compromises all of the attractive properties of projections.  Opening the door to reconciliation methods that change already coherent base forecast would seem to suggest an increase in the variability of the forecast.  This seems particularly perverse when the motivation for using a biased method in the first place is to reduce variance.

@@

	Alternatively, a more general purpose approach to bias correction is to simply estimate the bias by taking the sample mean of $\bm{y
	}_{t+h}-\hat{\bm{y}}_{t+h|t}$ for all $t+h$ in the training sample.  This can be then subtracted from future forecasts.  As stated in the discussion of MinT, in-sample errors are already used to estimate the optimal direction of projection.  As such we see no problems with using the same errors to bias correct.  Geometrically, the intuition is simple.  In top left panel in Figure \ref{fig:OthogonalVSOblique_projection}, the orange points are centered around the origin as would be expected from an unbiased forecast.  If forecasts are biased, then errors should simply be translated until they are centered at the origin.

@@

	Using an empirical application to forecast Australian domestic tourism flow, we illustrate the usefulness of projection based reconciliation in practice. Previous studies have pronounced that the reconciliation improves point forecast accuracy in domestic tourism flow in Australia (\cite{Athanasopoulos2009}, \cite{Hyndman2011}, \cite{WicEtAl2019}). However, our motivation in this study is to demonstrate how the bias correction methods discussed in previous section along with the projection-based reconciliation help to improve the forecast accuracy.

	\subsection{Data}

	We use ``overnight trips" as a measure of domestic tourism flow in Australia. Total ``overnight trips" in Australia can be disaggregated into 7 states, 27 zones and 75 regions forming a geographical hierarchy with $110$ total number of series and $75$ bottom level series. More information about the series of this hierarchy is given in Table \ref{table:A1} in the appendix. Data were obtained from the National Visitor Survey (NVS) which were collected through telephone interviews from an annual sample of $120,000$ Australian residents aged $15$ years or more. Data form a monthly series starting from January 1998 to December 2017 which gives a total of $240$ observations per series.

	As we can see from the time plots in Figure \ref{fig:Total_TSplots}, the total overnight trips has a strong seasonal pattern. Most overnight trips seems to be happening in January which is associated with the summer season in southern hemisphere. On the other hand the least trips are happening in February perhaps due to the end of summer holidays. We could also observe a slight downward trend in total overnight trips from 2005 to 2010 and then started increasing since 2010.

	Figure \ref{fig:States_Zones_Regs_TSplots} shows time plots for some selected series from states, zones and regions of the hierarchy. While observing the series in state level, we could see that Northern Territory(NT) has a different seasonal patterns compared to the other states. Highest overnight trips to NT happens during June - August where July being the peak. Lowest trips happens during December - February. This is perhaps Australians prefer to visit North of Australia during its dry season rather than in wet season. This pattern also reflect in zones and regions associated to NT as well as regions in north Queensland. All other states and their associated zones and regions show peak overnight trips in January.

	Further we noticed that the signal-to-noise ratio decreases with the level of disaggregation of the hierarchy. We can see much noisier series in regional and zone levels whereas the noise is comparatively stabilised in the upper levels. We have also observed that the overnight trips to `Adelaide Hills' has an anomalous observation on December-2002. We replace this observation with the average overnight trips on December-2001 and December-2003 for the same destination.

	Using this data we produce $h=1$ to $h=6$ month ahead forecasts based on a rolling window approach. First a training window of $100$ observations is considered from Jan-$1998$ to Apr-$2006$ and  forecasts produce for May-$2006$ to Oct-$2006$. Then we roll the training window one month at a time where the final forecast is produced for Dec-$2017$. This leads to $140 \quad 1$-step-ahead, $139 \quad 2$-step-ahead through $135 \quad 6$-step-ahead forecasts left for evaluation.

	\begin{figure}
		\centering
		\small
		\includegraphics[width = \textwidth]{Empirical-results/TS-plots/Total_TSplots.pdf}
		\caption{Total overnight trips are presented in log scale. Top panel shows the time plot. Bottom left panel shows the sub-series plot for each month whereas bottom right panel shows the seasonal plot coloured by year  }\label{fig:Total_TSplots}
	\end{figure}

	\begin{figure}
		\centering
		\small
		\includegraphics[width = \textwidth]{Empirical-results/TS-plots/States_Zones_Regs_TSplots.pdf}
		\caption{Time plot of overnight trips for some selected series from different disaggregate levels of the hierarchy. All values are presented in log scale. To avoid impact from the zero values we added a constant 1 to all observations}\label{fig:States_Zones_Regs_TSplots}
	\end{figure}

	\subsection{Base forecasts and reconciliation:}

	First we transform each series in the hierarchy to stabilise any variations in the data. We use two types of transformation, namely, log transformation and more general Box-Cox transformation. Equation (\ref{eq:BoxCox_transformation}) gives the mathematical formula for these transformations. A constant is added to each series to avoid the impact of zero observations when taking log transformations. We note here that the two transformations were applied separately to the series in the hierarchy and treated distinctly.

	\begin{equation} \label{eq:BoxCox_transformation}
	x_t = 
	\begin{cases} 
	\log(y_t) & \text{if log transformation, $\lambda = 0$} \\
	\frac{y_t^\lambda - 1}{\lambda}  & \text{if Box-Cox transformation, $\lambda \ne 0$} 
	\end{cases}
	\end{equation}

	The ``Guerrero" method \citep{guerrero1993time} implemented in \verb|BoxCox.lambda()| function in \verb|forecast| package in R software \citep{Rforecast} is use to select optimal $\lambda$ for Box-Cox transformation. For log transformation we simply choose $\lambda = 0$. Then  we fit univariate ARIMA models for the transformed series. \verb|auto.arima()| function in \verb|forecast| package is use to choose the best model that minimises the AIC. Using the fitted models, forecasts are produced for $6$ forecast horizons for each series in the hierarchy. These forecasts are then back-transformed using equation (\ref{eq:BoxCox_back-transformation}) to scale them back into the original space. However, the back transformed forecasts will be biased \citep{guerrero1993time}.

	\begin{equation} \label{eq:BoxCox_back-transformation}
	y_{t+h} = 
	\begin{cases} 
	\exp({x_{t+h}}) & \text{if log transformation, $\lambda = 0$} \\
	(\lambda x_{t+h} + 1)^{1/\lambda}  & \text{if Box-Cox transformation, $\lambda \ne 0$}
	\end{cases}
	\end{equation}

	Hence the reconciled forecasts that follow from these forecasts will also be biased. This is the exact scenario that we want to demonstrate in this study. As proposed before, we first adjust for the bias in base forecasts prior to the reconciliation. We use the de-biasing factor proposed by \cite{taylor1986retransformed} to calculate the back-transformed bias-adjusted forecasts. These are given in equation (\ref{eq:BoxCox_BT_biasadj}) .
